The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-20 dit-paper_ieee.tex
Removed emphasis on "strictly"
monoprocessor -> uniprocessor

		Furthermore, the following notations are used:
		\begin{itemize}
			\item $\tau = \{\tau_1, \cdots, \tau_{n}\}$
			\item $H = \operatorname{lcm}(T_1, \cdots, T_{n})$
			\item $O_{max} = \max (O_1, \cdots, O_{n})$
			\item An \emph{idle time} is an instant $t$ at which each job that arrived
			\emph{strictly} before $t$ has finished its execution.
			\item A \emph{busy period} is a time interval between two consecutive idle times in
			which at least one job is executing.
			\item The interval between the initial time ($t=0$) and the first
			idle time after $t=0$ is called the \emph{first busy period}.
		\end{itemize}

	\subsection{The DBF feasibility test}
		We recall the necessary and sufficient feasability condition on monoprocessor
		platforms based on the demand-bound function \cite{baruah1999generalized,
		baruah1990algorithms}.

>>>>

		Furthermore, the following notations are used:
		\begin{itemize}
			\item $\tau = \{\tau_1, \cdots, \tau_{n}\}$
			\item $H = \operatorname{lcm}(T_1, \cdots, T_{n})$
			\item $O_{max} = \max (O_1, \cdots, O_{n})$
			\item An \emph{idle time} is an instant $t$ at which each job that arrived
			strictly before $t$ has finished its execution.
			\item A \emph{busy period} is a time interval between two consecutive idle times in
			which at least one job is executing.
			\item The interval between the initial time ($t=0$) and the first
			idle time after $t=0$ is called the \emph{first busy period}.
		\end{itemize}

	\subsection{The DBF feasibility test}
		We recall the necessary and sufficient feasability condition on uniprocessor
		platforms based on the demand-bound function \cite{baruah1999generalized,
		baruah1990algorithms}.
